|

### 2023-06-15 paper/article.qmd
finished result part 1

@@

Focusing on **protest goals** first.
Table 3 analyzes protest goals compared to the reference, political protests.
Hypothesis H1a, proposing a hierarchy of social struggle that influences the use of *delegitimising* frames, is unsupported:
no significant effect is found on the use of these frames among different goals.
In other words, delegitimising frames are used similarly across all goals, refuting a social struggle hierarchy in UK newspaper coverage.

In contrast, Hypothesis H1b, regarding a social struggle hierarchy influencing *legitimising* framing, is partially supported.
Labour protests (AME: 6%) and social-issue protests (AME: 16%) are more likely to receive legitimising coverage than political protests.
For instance, a typical labour issue, like a protest for police salaries, has a 6% higher chance of being reported with legitimising framing, and a protest against tuition fees (a social issue) is 16% more likely to be legitimised compared to political protests.
However, anti-war and police protests show no significant difference from the reference category.
H1b can this be accepted only partially:
protests with certain goals are more likely to be covered with a legitimising frame than others.
However, the specific hierarchy in the UK appears different from what has been found previously for the US context [@kilgoHierarchy2019].
Specifically, protests against police brutality have the least chance of legitimising coverage.
Then come political protests, anti-war protests, labour protests, and finally, social-issue protests with the highest probability of legitimising framing.
However, there is uncertainty in this hierarchy as political and anti-war protests show nearly identical probabilities of legitimising framing.

>>>>

## (De)Legitimising Framing

@@

Focusing on **protest goals** first.
Table 3 analyzes protest goals compared to the reference, political protests.
Hypothesis H1a, proposing a hierarchy of social struggle that influences the use of **delegitimising** frames, is unsupported:
no significant effect is found on the use of these frames among different goals.
In other words, delegitimising frames are used similarly across all goals, refuting a social struggle hierarchy in UK newspaper coverage.
However, as each article can contain one or multiple delegitimising or legitimising frames or neither, this result has no impact on H1b , as the two models are independentl from each other.

In fact H1b, regarding a social struggle hierarchy influencing **legitimising** framing, is partially supported.
Labour protests (AME: 6%) and social-issue protests (AME: 16%) are more likely to receive legitimising coverage than political protests.
For instance, a typical labour issue, like a protest for police salaries, has a 6% higher chance of being reported with legitimising framing, and a protest against tuition fees (a social issue) is 16% more likely to be legitimised compared to political protests.
However, anti-war and police protests show no significant difference from the reference category.
H1b can this be accepted only partially:
protests with certain goals are more likely to be covered with a legitimising frame than others.
However, the specific hierarchy in the UK appears different from what has been found previously for the US context [@kilgoHierarchy2019].
Specifically, protests against police brutality have the least chance of legitimising coverage.
Then come political protests, anti-war protests, labour protests, and finally, social-issue protests with the highest probability of legitimising framing.
However, there is uncertainty in this hierarchy as political and anti-war protests show nearly identical probabilities of legitimising framing.

As explained before, the relation between violent **tactics** and less favourable coverage of the protest is well established.
Table 3 and @fig-margtwoframes confirm this connection.
Violence has a significant effect in the expected directions in both the models for legitimising and delegitimising frames.
When there is violence, the probability that a delegitimising frame is used increases by `r marg("violent protest", unit = "percent")`.
Conversely, when protesters remain peaceful, the likelihood for usage of legitimising frames increases by `r marg("violent protest", model = "legitimising", unit = "percent")`.
In other words, when protests become violent, it is a lot more likely that they will receive both more delegitimising and less legitimising coverage.
Consequently, both H2a and H2b are accepted.
Furthermore, some authors suggest that protests might use violent tactics to attract more media coverage [e.g., @boyleAdherenceProtestParadigm2012].
This might still make sense, but given the significantly more negative coverage, media exposure for a specific protest needs to be quite high for this trade-off to make sense.

The notion that the **state's response** matters for protest coverage is based on findings by @WasowSeeding2020, which suggest that in cases with violent reactions towards peaceful protest, coverage will be more legitimising.
However, the findings here show the exact opposite effect:
it appears that legitimising framing is *less* likely by `r marg("repression of peaceful p.", model = "legitimising", unit = "percent")` for events in which the state uses repressive tactics against peaceful protesters.
This means that H3 has to be rejected.
But why?

It must be noted that the effect here is not driven by *violent* state responses to peaceful protest, as was the case in the study by @WasowSeeding2020.
There were no instances of violent state response towards peaceful protest in the UK data set --- or at least they have not been coded by @ClarkMMPdata2019.
Instead the variable *state repression of peaceful protest* reflects *arrests* of peaceful protesters here.
The findings are nevertheless striking; it means that when protesters are arrested, this has a significantly negative impact on the probability of receiving coverage framed in a legitimising way, even if they remain peaceful.

On the outlet level, three factors are taken into account: *newspaper ideology*, *ideological divide* and *newspaper type*.
Despite a strong theoretical underpinning, **newspaper ideology** shows no significant effect in either of the two models in Table 3.
This means both H4a and H4b have to be rejected.
The outcome is surprising, especially since the UK case was specifically chosen because the ideological divide between outlets is more distinct than in the US or elsewhere [@kuhnPoliticsMediaBritain2007; @hallinComparingMediaSystems2004] and has been suggested to shape UK coverage of protest as well [@gavinPressTelevisionBritish2007].

Instead, one might assume that **ideological divide** might instead explain coverage.
In fact, during the manual part of the content analysis, it became apparent that some protests were supported openly by right-leaning news outlets, such as the 2000 fuel protests or protests against fox hunting legislation introduced in 2005, while left newspapers were much more critical.
So maybe ideological conflict, rather than newspaper ideology, matters for reporting?
Again, the answer is no.
Both models show no significant difference between ideological congruence and conflict between protesters and newspaper.
Both H5a and H5b are therefore rejected.
This means that while there is anecdotal evidence that left-wing media are more critical of right-wing protest and vice versa, the phenomenon is not widespread enough to be picked up by systematic statistical analysis.

Surprisingly, the *ideological ambiguity* category, which comprises very heterogeneous events ranging from protest against business practices of a company to ex-pat protests about issues abroad, has a positive effect in both models.
It is thus not straightforward to understand why they are more likely to be covered with legitimising frames *as well* as delegitimising frames.
One possible explanation is that journalists feel less constrained to voice their opinion when an issue hasn't been discussed along party lines (yet).

Moving on to the *type of newspaper*, we can see that this indicator only has an effect in the model for legitimising frames:
it is significantly less likely for tabloid news media to use legitimising frames than it is for broadsheet outlets.
Specifically, the probability that a legitimising frame is used is `r marg("tabloid newspaper", model = "legitimising", unit = "points")` percentage points lower on average when an article is published in a tabloid newspaper.
For delegitimising frames, it seems that both types of media outlets are equally likely to use delegitimising frames.
Hypothesis H6a is therefore rejected, while H6b is accepted.

Two of the tested factors were related to **timing** of events.
The model for delegitimising frames shows that as more days pass after the beginning of a protest, it becomes more likely that articles will contain a delegitimising frame.
The AME shows that the effect is one of the largest at a -`r marg("days from start", unit = "percent")`.
However, note that *days from start* was one of the two variables that were rescaled so that the minimum was 0 and the maximum was one.
The AME here, therefore, displays the change in probability when going from the minimum of 7 days before, to the maximum of 81 days after the start of a protest.
The relation is shown in @fig-dfspred and it becomes clear that it is not  a linear one.
Instead, we see the highest average probabilities that one of the delegitimising frames is used in the first week after a protest, with lower values before and after.
Average probabilities decrease for a while but increase again after about 8 weeks --- a time frame in which only a few high-profile and long-lasting protests still receive any coverage at all.
It seems then that delegitimising frames are most compelling to journalists in the direct aftermath of an event.
This confirms the expectation in H8a.

```{r}
#| label: fig-dfspred
#| fig-cap: Predicted Probabilities of Using a Delegitimising Frame Before and After the Start of a Protest (dotted red line)
days_pred <- prediction::prediction(models$model_logit_dele_mlm) %>%
  # scale back to original values
  mutate(days_since_start = scales::rescale(
    days_since_start,
    to = c(-7, 81))
  )
days_pred %>%
  ggplot(aes(x = days_since_start, y = fitted)) +
  geom_point(colour = "#939597", alpha = 0.2) +
  geom_smooth(method = "loess", formula = "y ~ x", se = FALSE, colour = "black") +
  geom_vline(xintercept = 0, linetype = "dashed", colour = "#F65058") +
  scale_x_continuous(breaks = c(-7, 0, 5, 10, 20, 30, 40, 50, 60, 70, 80)) +
  labs(y = NULL, x = NULL)
```

As was already shown in @gruberTrouble2023, the year doesn't affect the probability of delegitimising frames but does increase the probability that legitimising frames being used.^[
Although @gruberTrouble2023 uses the year in which an article was published while here it is the year of the protest event itself --- which is identical for most articles though. Note also that articles were excluded if they could not be matched with any event in the MMP data.
]
The full model, therefore, confirms this previous finding as the year has a significant positive effect on the probability that legitimising framing is used, suggesting legitimising frames become more salient over time.
Specifically, comparing the last year, 2017, in the dataset to the first year, 1992, legitimising framing has become `r marg("Year of protest (since 1992)", model = "legitimising", unit = "percent")` more likely on average.
H8b is this confirmed.

## Unpacking Frame Usage {#sec:regall}

Coming soon...
